### 2016-01-04 doc/tutorial/detailed.Rmd
restructuring

>>>>

# Advanced

In some cases you might to want to modify the internal object corresponding to a method. **SVMBridge** stores these in its own environment. You can access these Conveniently by using ```getSVMObject()```. After modifying them, you can store the object back by overwriting ```setSVMObject()``, so that the SVMBridge can work with it. Notice that broken objects might lead to unforseen behaviour and crashes.
